\documentclass{book}
\newcommand{\BE}{\begin{enumerate}\item}
\newcommand{\EE}{\end{enumerate}}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\EI}{\end{itemize}}
\newcommand{\I}{\item}
\newcommand{\Q}[2]{\begin{quote} \textbf{#2 \center{#1}}\end{quote}}
\begin{document}
\tableofcontents
\part{On the existence of God}
\chapter{Introduction}
\section{Psalm 14:1}
\Q{Psalm 14:1}
    {The fool has said in his heart,\\
    ``There is no God,''\\
    They are corrupt, \\
    They have done abominable works, \\
    There is none who does good.}
\BI Romans 3:9 applies this text to both Gentiles and Jews
    by quoting Psalm 14:1-3 in Romans 3:10-12.
\I  The Psalmist talks about the corruption of the atheist's soul,
    and then the corruption of his practice.  \EI

\subsection{\emph{The fool}}
\BI A wicked man.
\I  Root of Hebrew word signifies the extinction of life
    in men, animals and plants.
\I  A fool has lost wisdom, a right notion of God.
\I  He is dead in sin. \EI

\subsection{\emph{Said in his heart}}
\BI Thinks in himself.
    \Q{Psalm 10:11,13}
    {He has said in his heart, \\
    ``God has forgotten; \\
    He hides His face; \\
    He will never see.'' \\
    \ldots \\
    Why do the wicked renounce God? \\
    He has said in his heart, \\
    ``You will not require an account.''}

\I  Cannot eliminate all thoughts of God, but seeks to. \EI

\subsection{\emph{``There is no God''}}
\BI Hebrew word used for God is \emph{Eloahia},
    the providence of God, God as judge.
\I  Denies not God's existence but His providence.
\I  Three classes of atheism:
    \BI denying God's existence,
    \I  denying God's providence (or His working in this world), and 
    \I  denying God's nature (or character). \EI
\I  Denying His providence \emph{is} denying His existence
    because it is a denying of His glory.
\I  They do this so that they may be free to sin. \EI

\subsection{\emph{They are corrupt, they have done abominable works,
            there is none who does good}}
\BI The denier of God is in singular (\emph{the} fool),
    but those who are corrupt are in plural.
\I  Points to a widespread, secret atheism in all men.
\I  A partial atheism is the source of all evil and sin.
    \BI God is the source of purity, when He is denied,
        men inevitably become polluted in soul and body. \EI
\I  No man is exempt from this kind of atheism.
    \Q{Titus 1:16}
    {They profess to know God, but in works they deny Him,
    being abominable, disobedient, and disqualified for 
    every good work.} \EI

\subsection{Summary of Psalm 14:1}
\BI In summary, the text describes man's corruption.
\BE Corruption of the mind in that the atheist is a fool.
\I  Corruption of the faculties in 
    \BE sins of comission (being corrupt, abominable), and
    \I  sins of omissions (there is none that does good). \EE 
\EE
\I  The corruption of the mind is the cause, and 
    the corruption of the faculties is the effect. \EI

\section{Outline of argument}
\BE To deny God is a great folly.
\I  Practical atheism is natural to fallen man.
\I  A partial atheism  is the source of all wickedness 
    in the world.  \EE

\subsection{The need to prove that God exists}
\BE The growth of atheism.
    \BI Atheism is flourishing in modern times.
    \I  Although written so deeply within us,
        yet suppressed so strongly by us (Romans 1:18). \EI
\I  The existence of God is the foundation of all religion.
    \BI All worship, service, and hope would be for nothing
        if God did not exist. \EI
\I  We should know why we believe that God is.
    \BI To say that there is a God but not know why,
        or not know the arguments for his existence,
        is almost saying that there is no God. \EI
\I  We must fight the secret atheism that is in all of us.
    \BI We must daily be reminded of who God is
        in order to combat our flesh. \EI
\I  Arguments of logic for God's existence are profitable 
    for the Christian, in that they buttress our love for Him. \EE

\subsection{The existence of God is evidenced by reason}
\BE God has revealed Himself in creation as well as His word.
    \Q{Romans 1:19-20}
    {\ldots because what may be known of God is manifest in them, 
    for God has shown it to them. 
    For since the creation of the world His invisible attributes are
    clearly seen, being understood by the things that are made, 
    even His eternal power and Godhead, 
    so that they are without excuse.}
\I  There is a Scriptural pattern to learn of God by looking at
    His creation.
    \BI The apostles reasoned for God from His creation
        (Romans 1:19; Acts 14:16-17),
        even among the intellectually elite
        philosophers of Athens (Acts 17:27, 29).  
        Thus, such reasoning must be solid and without contradiction.
    \I  God also justified His actions by arguing from creation
        with Job.
    \I  God has never done a miracle to prove His existence,
        only to confirm divine truth.
        Therefore His creation must be proof enough of 
        His existence. \EI 
\EE

% \section{To deny God is a great folly}
% \subsection{All nations throughout the ages have acknowledged
%     that God is}

\chapter{Demonstration}
\section{Acknowledged by every nation, at every time}
\subsection{Every nation assents to the existence of God}
\BE No nation exempt
\I  Multiplicity of idols does not deny, but confirm this
\I  Many disputes in the world, but not over God's existence
\I  Individual atheists? \EE
\subsection{God is the constant consent of all nations}
\BE Amidst all the changes, the belief in God is unchanged
\I  Men would have rooted out the idea of God, if possible
\I  By the Scripture, Satan does not try to disprove this \EE
\subsection{This consent is natural and innate}
\BE Not by mere tradition
\I  Nor by some conspiracy
    \BI How could this be pulled off?
    \I  How could this last so long? \EI
\I  Not introduced by fear \EE
\section{Acknowledged by every creature and thing}
\subsection{In their production}
\BE All things had a beginning
    \BI Time cannot be infinite
    \I  Generations of life could not be from eternity \EI
\I  Nothing can make itself
    \BI Nothing can act before it is
    \I  That which does not understand itself could not make itself
    \I  If so, why would man limit himself?
    \I  If so, why can't man preserve himself?
    \I  If so, why not create himself earlier? \EI
\I  No creature could make the world
\I  There must be a first cause, God!
    \BI This God must exist
    \I  He must be perfect \EI
\EE
\subsection{In the harmony of creation}
\BE In the linking of contrary qualities together
\I  In the subserviency of one thing to another
    \BI Of heavenly bodies
    \I  Of the lower world (earth and sea)
    \I  To man (centers in man)
    \I  Regular and uniform
    \I  Constant \EI
\I  The varity of creation \EE
\subsection{In that creatures act to their own end}
\BE Different creatures survive in different ways
\I  They know now their end
\I  Therefore there must be a superior nature \EE
\subsection{In their preservation}
\section{Acknowledged by man's own nature}
\subsection{In his body}
\BE Order and usefulness of every part
    \BI Heart
    \I  Mouth
    \I  Brain
    \I  Ear
    \I  Eye
    \I  Tongue \EI
\I  Differences between men \EE
\subsection{In his soul}
\BE It's vast capactiy
\I  It's quickness
\I  Union of soul and body \EE
\subsection{In his conscience}
\BE Knowledge of good and evil
\I  Conviction of sin
    \BI Universal
    \I  Conscience is highly operative in secret sin
    \I  Cannot be shaken off \EI
\EE
\subsection{In his ongoing dissatisfaction}
\section{Achnowledged by extraordinary phenomena}
\subsection{In judgements}
\subsection{In miracles}
\subsection{In prophecies}

\chapter{Use}
\section{Atheism is a danger to the world and to the atheist himself}
\BE To the world
    \BI Root out foundation of government
    \I  Introduce evil \EI
\I  To the atheist himself \EE
\section{It is lamentable that there are so many atheists now}
\BE Atheism is unprovable
\I  All creatures fight against the atheist
\I  Emergency reveals an inward belief in God
\I  What is the goal of atheism?
\I  Why choose such danger for such goals?
\I  Can anyone say he has sought God enough? \EE
\section{It is our wisdom to firmly know that God is}
\BE We need this to worship Him
\I  We need this to order our lives
\I  For comfort
\I  To believe Scripture
    \BI Study God in creation as well as Scripture
    \I  See God in our own experiences \EI
\EE
\section{To not worship God is just as bad as atheism}
\end{document}

